Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-14 Paper/Manuscript.tex
Thanks and out with 3-country method

\author[1]{Guillaume Corlay}
\author[2]{Stéphane Dupraz}
\author[3]{Claire Labonne}
\author[1]{Anne Muller}
\author[4]{Céline Antonin}
\author[5]{Guillaume Daudin\footnote{Corresponding author: guillaume.daudin@dauphine.fr}}
\affil[1] {ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff, FRANCE}
\affil[2] {Columbia University, 10025 New York NY, USA}
\affil[3] { Paris School of Economics / Université Paris 1 Panthéon Sorbonne -- ACPR - Banque de France, 75009, PARIS, FRANCE}
\affil[4] {Sciences Po, Observatoire Français des Conjonctures Économiques (OFCE), 75007, PARIS, FRANCE}
\affil[5] {Université Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE

@@

\cite{AW2003}'s model can be used to calculate the aggregate
trade costs a single country faces in its trade with all
its trading partners. Indeed, using a two-countries model where
all trade partners of country $i$ are treated as one single
country provides an aggregate measure of trade costs that does
not rely on any \textit{ad hoc} aggregation method but instead on
microfoundations. Since all trade flows data are not available,
it is also possible to use a three-countries model, with
country $i$, its trading partners present in the data, and the
rest of the world.

@@

where $x_{ip}$ and $x_{pi}$ are respectively real exports and
imports of $i$ from and to its trade partners in the data, and
$x_{pp}$ is the volume of trade within and between the trading
partners present in the data. This `domestic trade' variable
now
includes cross-border trade.\\

>>>>

\author[1]{Guillaume Corlay}
\author[2]{Stéphane Dupraz}
\author[3]{Claire Labonne}
\author[1]{Anne Muller}
\author[4]{Céline Antonin}
\author[5]{Guillaume Daudin\footnote{Corresponding author: guillaume.daudin@dauphine.fr. The authors thank Marc Adam, Marcelo Olarreaga and anonymous referees for their comments and questions}}
\affil[1] {ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff, FRANCE}
\affil[2] {Columbia University, 10025 New York NY, USA}
\affil[3] { Paris School of Economics / Université Paris 1 Panthéon Sorbonne -- ACPR - Banque de France, 75009, PARIS, FRANCE}
\affil[4] {Sciences Po, Observatoire Français des Conjonctures Économiques (OFCE), 75007, PARIS, FRANCE}
\affil[5] {Université Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE

@@

\cite{AW2003}'s model can be used to calculate the aggregate
trade costs a single country faces in its trade with all
its trading partners. Indeed, using a two-countries model where
all trade partners of country $i$ are treated as one single
country provides an aggregate measure of trade costs that does
not rely on any \textit{ad hoc} aggregation method but instead on
microfoundations.

@@

where $x_{ip}$ and $x_{pi}$ are respectively real exports and
imports of $i$ from and to its trade partners in the data, and
$x_{pp}$ is the volume of trade within and between the trading
partners present in the data. This `domestic trade' variable
now
includes cross-border trade. The problem with this method is that it is very data-intensive. It requires the knowledge of all bilateral trade flows between the countries in the data. \\
